Adapting bootstrap to our problem

### 2024-07-10 adapt_boot.Rmd
Adapted bootstrap is fine

---
title: "Adapting bootstrap to our problem"
output: html_document
date: "2024-07-10"
---

@@

@@

```{r}
plot(x = random_points[, 1], y = random_points$var, xlab = "x", main = "Points as a function of x", las = 1)
```

```{r}
plot(x = random_points[, 2], y = random_points$var, xlab = "y", main = "Points as a function of y", las = 1)
```

@@

@@

    tot_mean <- append(tot_mean, as.numeric(abs(mean(est_boot_2)-30942) <  abs(mean(est_boot_1)-30942)))
    # 1: the second method is better
    tot_var <- append(tot_var, as.numeric(var(est_boot_2) <  var(est_boot_1)))
    # 1: the second method is better
    b <- b+1
  }
  return(tot_mean, tot_var)
}
```

```{r}
comparison(100, 500)
```

```{r}
sum(tot_mean)
```

```{r}
sum(tot_var)
```

>>>>

---
title: "Adapting bootstrap to our problem"
output: pdf_document
date: "2024-07-10"
---

@@

The goal of this document is to create another bootstrap function that is adapted to the problem of continuous sampling with a grid. Indeed, we want a bootstrap function that takes into account the regularity of the sampling which is induced by the grid.

@@

@@

Here, two methods are used: a naive one and an adapted one.

@@

    tot_mean <- append(tot_mean, as.numeric(abs(mean(est_boot_2)-30942) <  abs(mean(est_boot_1)-30942))*2-1)
    # 1: the second method is better
    tot_var <- append(tot_var, as.numeric(var(est_boot_2) <  var(est_boot_1))*2-1)
    # 1: the second method is better
    b <- b+1
  }
  return(list(tot_mean, tot_var))
}
```

```{r}
res <- comparison(100, 500)
```

```{r}
# If it is positive, the second method is the best to estimate the total
sum(res[[1]])
# 10 e.g.
# 18
```

```{r}
# If it is positive, the second method is the best to minimize the variance
sum(res[[2]])
# 2 e.g.
# 12
```

# Conclusion

Adapting bootstrap to the problem seems relevant.
